Unnecessarily Complicated Research Title

### 2020-10-29 Chapter4/4_4_results.tex
chapter_4_passed

Figures~\ref{fig:4_4_matrixEvo} and \ref{fig:4_4_matrixCar2Go} detail the spatial-temporal demand for Evo and Car2Go by presenting their origin-destination matrix mapped on 31 city areas as defined by the metropolitan city of Vancouver. To enhance the visual effects, we normalized the previous heat-maps values to a scale between 0-1, using the min-max method. Moreover, due to space constraint, this work shows the origin-destination matrix at a specific hour, i.e., at 4\,PM.
In general, the users tend to start and end a trip at the same location. It appears that during working days, users tend to use a shared car  returning it to the same region where they start (likely where they are working or living). However, for both services, a non-negligible probability to spread services along all city area is noticeable. 
Moreover, we also note that some regions serve as hubs. This is more notable for Evo service. As shown in figure~\ref{fig:4_4_matrixEvo}, the downtown area serves as a hub to start trips to almost all other regions. The opposite (a high tendency to start a trip ending at downtown) trend is not present. As a consequence, service may become unbalanced and, from time to time, service maintenance should relocate vehicles from a region to another, to accommodate the daily demand.

@@

Finally, figure~\ref{fig:4_4_idle_all_eCDF}, presents vehicle idle periods distribution.  Power~log~normal\footnote{Cumulative distribution function (CDF) of the Power~log~normal distribution: $F(x,c,s,\beta,\delta)=1-\left(\frac{1}{\sqrt{2\pi}}\int_{-\infty}^{-log((x-\beta)/\delta)/s}e^{-t^{2}/2}dt\right)^{c}$}, Burr and Mielke's~Beta$-$Kappa distributions best fit the idle data, for all three datasets. Table~\ref{table:fit_idle} presents the distribution parameters. 
Again, Modo presents a distinct behavior from the other two services. The longer idle period for Modo vehicles corroborates to our previous observations. Indeed, the demand for car-sharing varies over the city during a day. While users in Evo and Car2Go can park anywhere, they contribute to spreading cars over the city. For example, at least 75\% of cars in Modo remains idle for periods longer than 2 hours. For the other two services, no more than 20\% of vehicles remains idle for the same period.

In sum, our analysis shows that the free-floating and one-way car-sharing systems have similar characteristics. They are mostly used for short/medium period travels, while the two-way system is mostly used for medium to long travels. 
Moreover, Evo and Car2Go dynamically spread car over the city, turning the car's idle periods shorter. The longer number of shorter travels, associated with the shorter idle periods, may indicate a more profitable service.

>>>>

Figures~\ref{fig:4_4_matrixEvo} and \ref{fig:4_4_matrixCar2Go} detail the spatial-temporal demand for Evo and Car2Go by presenting their origin-destination matrix mapped on 31 city areas as defined by the metropolitan city of Vancouver. To enhance the visual effects, we normalized the previous heat-maps values to a scale between 0-1, using the min-max method. Moreover, due to space constraint, this work shows the origin-destination matrix at a specific hour, i.e., at 4\,PM.
In general, the users tend to start and end a trip at the same location. It appears that during working days, users tend to use a shared car  returning it to the same region where they start (likely where they are working or living). However, for both services, a non-negligible probability to spread services along all city area is noticeable. 
Moreover, it is possible to note that some regions serve as hubs. This is more notable for Evo service. As shown in figure~\ref{fig:4_4_matrixEvo}, the downtown area serves as a hub to start trips to almost all other regions. The opposite (a high tendency to start a trip ending at downtown) trend is not present. As a consequence, service may become unbalanced and, from time to time, service maintenance should relocate vehicles from a region to another, to accommodate the daily demand.

@@

Finally, figure~\ref{fig:4_4_idle_all_eCDF}, presents vehicle idle periods distribution.  Power~log~normal\footnote{Cumulative distribution function (CDF) of the Power~log~normal distribution: $F(x,c,s,\beta,\delta)=1-\left(\frac{1}{\sqrt{2\pi}}\int_{-\infty}^{-log((x-\beta)/\delta)/s}e^{-t^{2}/2}dt\right)^{c}$}, Burr and Mielke's~Beta$-$Kappa distributions best fit the idle data, for all three datasets. Table~\ref{table:fit_idle} presents the distribution parameters. 
Again, Modo presents a distinct behavior from the other two services. The longer idle period for Modo vehicles corroborates to the previous observations. Indeed, the demand for car-sharing varies over the city during a day. While users in Evo and Car2Go can park anywhere, they contribute to spreading cars over the city. For example, at least 75\% of cars in Modo remains idle for periods longer than 2 hours. For the other two services, no more than 20\% of vehicles remains idle for the same period.

In sum, the analysis shows that the free-floating and one-way car-sharing systems have similar characteristics. They are mostly used for short/medium period travels, while the two-way system is mostly used for medium to long travels. 
Moreover, Evo and Car2Go dynamically spread car over the city, turning the car's idle periods shorter. The longer number of shorter travels, associated with the shorter idle periods, may indicate a more profitable service.
